Edge sign prediction in general graphs and Correlation Clustering

### 2017-12-12 cc/gtx_related.tex
fix missing ref

We may then want to minimize the stretch of:
\begin{enumerate}[1),nosep]%,leftmargin=*]
  \item some pairs of nodes. That is, given $L$ and $R$ in $V$, minimize $\sum_{u \in L, v\in R}
    \estr(u,v)$
  \item all pairs of nodes corresponding to edges of $G$, \ie{} minimize $\sum_{(u,v) \in E}
    \estr(u,v)$
  \item all pairs of nodes, \ie{}  minimize $\sum_{(u,v) \in V^2} \estr(u,v)$
\end{enumerate}
Note that for an unweighted graph, the second problem reduces to minimizing $\sum_{(u,v) \in E}
|\pathhuv|$. If furthermore $H$ is tree, this is equivalent to minimize the second term of equation
\eqref{eq:stretch_mistakes}. Therefore we focus mainly of that definition of stretch, and consider
the other two only briefly.

>>>>

We may then want to minimize the stretch of:
\begin{enumerate}[1),nosep]%,leftmargin=*]
  \item some pairs of nodes. That is, given $L$ and $R$ in $V$, minimize $\sum_{u \in L, v\in R}
    \estr(u,v)$
  \item all pairs of nodes corresponding to edges of $G$, \ie{} minimize $\sum_{(u,v) \in E}
    \estr(u,v)$
  \item all pairs of nodes, \ie{}  minimize $\sum_{(u,v) \in V^2} \estr(u,v)$
\end{enumerate}
Note that for unweighted graphs, the second problem reduces to minimizing
\begin{equation}
  \label{eq:test_stretch_def}
  \estr(H) = \sum_{(u,v) \in E} |\pathhuv|.
\end{equation}
If furthermore $H$ is tree, this is equivalent to minimize the second term of equation
\eqref{eq:stretch_mistakes}. Therefore we focus mainly of that definition of stretch, and consider
the other two only briefly.

### 2017-12-12 conclusion/main.tex
fix missing ref

  \item Finally, in \autoref{chap:edge}, we considered the case where there are more than two types
    of edge. This means that instead of signed graphs, our input shifted to multilayer graphs, which
    are also ubiquitous to describe real world phenomena. Moreover, we modified the learning
    setting, so that no edge label are available, but instead nodes carry a profile vector. However,
    our goal remained to predict edge type, in what could then be described as a clustering problem
    with side information and interpretability requirements. In order to do so, we first defined a
    similarity between nodes, which accommodate both heterophily and homophily. We then formulate
    the problem as simultaneously finding $k$ special vectors called directions, and assigning one
    of them to every edge in order to maximize a scalar \emph{goodness} function. After introducing
    baselines oblivious of the graph topology, we added constraints resulting in one vectorial and
    one matricial optimization objectives. Finally, we showed on synthetic data how those methods
    can recover the planted ground truth.

@@

In this paragraph, we present the reciprocal recommendation problem~\autocite{Pizzato2013}. As we
shall see, it incorporates aspects from all the problems we discussed previously. Broadly speaking,
given two sets of users $L$ and $R$, we want to recommend users in $R$ to users in $L$, and vice
versa. These recommendations are based on mutual interest, but in most cases there is an asymmetry
between the two groups. To better illustrate this general definition, we now give some concrete
examples.

\begin{itemize}
  \item One recent application that quickly rose to prominence is online
    dating~\autocites{Krzywicki2015}{Xia2016a}{Alanazi}. In the most common case, users are divided
    between men and women, and we want to recommend users of the opposite gender in order to create
    couples. A well known example of such a system is Tinder~\autocite{TinderDesc16}.
  \item In another domain, we can also match job seekers and
    employers~\autocites{Siting2012}{Hong2013}{Kille2015}.
  \item As a specific case in point, \textcite{Zhang2016a} propose a method to match prospective PhD
    students and their future supervisors.
  \item In large organizations or associations, having a mentor is usually beneficial for
    both employees and employers~\autocite{mentorBenef04} and finding mentee/mentor pairs can be
    cast as a reciprocal recommendation problem~\autocite{OSSMentors12}.
    %\url{http://ieeexplore.ieee.org/abstract/document/7207130/}
  \item After moving to their new jobs, people also need a place to live. Again, we can match
    tenants and landlords, or people to share a flat.
  \item Finally, in a more critical setting, finding relevant matches between patients and organ
    donors can improve the success of transplants~\autocite{patientDonor17}.
\end{itemize}

>>>>

  \item Finally, in \autoref{chap:vector}, we considered the case where there are more than two types
    of edge. This means that instead of signed graphs, our input shifted to multilayer graphs, which
    are also ubiquitous to describe real world phenomena. Moreover, we modified the learning
    setting, so that no edge label are available, but instead nodes carry a profile vector. However,
    our goal remained to predict edge type, in what could then be described as a clustering problem
    with side information and interpretability requirements. In order to do so, we first defined a
    similarity between nodes, which accommodate both heterophily and homophily. We then formulate
    the problem as simultaneously finding $k$ special vectors called directions, and assigning one
    of them to every edge in order to maximize a scalar \emph{goodness} function. After introducing
    baselines oblivious of the graph topology, we added constraints resulting in one vectorial and
    one matricial optimization objectives. Finally, we showed on synthetic data how those methods
    can recover the planted ground truth.

@@

We first present a task tightly related to our edge characterization problem, namely the reciprocal
recommendation problem~\autocite{Pizzato2013}. As we shall see, it indeed incorporates aspects from
all the problems we discussed previously, along with new constraints. Broadly speaking,
given two sets of users $L$ and $R$, we want to recommend users in $R$ to users in $L$, and vice
versa. These recommendations are based on mutual interest, but in most cases there is an asymmetry
between the two groups. To better illustrate this general definition, we now give some concrete
examples.

\begin{itemize}[leftmargin=*]
  \item One recent application that quickly rose to prominence is online
    dating~\autocites{Krzywicki2015}{Xia2016a}{Alanazi}. In the most common case, users are divided
    between men and women, and we want to recommend users of the opposite gender in order to create
    couples. A well known example of such a system is Tinder~\autocite{TinderDesc16}.
  \item In another domain, we can also match job seekers and
    employers~\autocites{Siting2012}{Hong2013}{Kille2015}.
  \item As a specific case in point, \textcite{Zhang2016a} propose a method to match prospective PhD
    students and their future supervisors.
  \item In large organizations or associations, having a mentor is usually beneficial for
    both employees and employers~\autocite{mentorBenef04} and finding mentee/mentor pairs can be
    cast as a reciprocal recommendation problem~\autocite{OSSMentors12}.
    %\url{http://ieeexplore.ieee.org/abstract/document/7207130/}
  \item After moving to their new jobs, people also need a place to live. Again, we can match
    tenants and landlords, or people to share a flat.
  \item Finally, in a more critical setting, finding relevant matches between patients and organ
    donors can improve the success of transplants~\autocite{patientDonor17}.
\end{itemize}
